Global adjoint tomography -- Model GLAD-M25

### 2019-01-25 main.tex
add p phase measurements hist

@@

{\color{red} Wenjie: Also include the P arrival measurements here.}

>>>>

Fig~\ref{fig:P_phase_hist} shows histograms of the phase measurements of first P
arrivals in 4 of the body wave measurement categories. All the
categories show consistent reduction in both mean and variance values. 
Even though there are many kinds of phases assimilated  and
P arrivals only contribute ~8\% of the overall measurements,
the histogram shows we are still doing a good job at minimizing the
misfit of the P arrivals.

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{figures/dt_histogram_P.pdf}
  \caption{Histograms of phase measurements of P arrivals in four measurement categories for S362ANI combined with CRUST2.0 (M00, \textbf{Black}), GLAD-M15 (M15, \textbf{{\color{ForestGreen} Green}}) and GLAD-M25 (M25, \textbf{{\color{Red} Red}}). Other settings are the same as Fig.~\ref{fig:phase_hist}. }
  \label{fig:P_phase_hist}
\end{figure}

@@
